Review: Crop adaptation through introgression from wild relatives

### 2017-04-10 paper.tex
paste Table1 and Figure1 into the paper.tex

\noindent{\textbf{Table 1:} List and brief description of recently developed methods and examples of empirical studies employing these methods.}

\noindent{\textbf{Figure 1}: Wing coloration patterns in \emph{Heliconius} and evidence for introgression across species based on Patterson's \emph{D}-statistic; adapted from \cite{Heliconius2012}.}

%\lwang{In this part, maybe better to incorporate this reference, Detection and Polarization of Introgression in a Five-Taxon Phylogeny; and a new method published this year RND\_min Powerful methods for detecting introgressed regions from population genomic data; I donot know if we should also include G\_min, that is the statistic we tried that didnot work well for us: A new method to scan genomes for introgression in a secondary contact model. I put the three in the bib file.}

>>>>

%Table1
\begin{figure}
\begin{tabular}{l|l|l|l}
\bf methods	& \bf data type  &	\bf reference &  \bf empirical studies  \\ \hline

\emph{\bf chromosome paiting} &   &   &   \\
Hapmix	& phased haplotype; reference panel		& Price et al. 2009	&  Hufford et al. 2013;  Suarez et al. 2016 \\ 
RASPberry &	phased haplotype &	Wegmann et al. 2011	 & Christe et al. 2016 \\
MultiMix & phased/unphased genotype; reference panel &	Churchhouse and Marchini 2013 &	Eyheramendy et al. 2015 \\
PCAdmix	 & phased haplotype	 & Brisbin et al. 2012	 & Moreno et al. 2014; Pugach et al. 2016 \\
LAMP  &	phased haplotypes; reference panel	 & Sankararaman et al. 2008	 & Patterson et al. 2012 \\

\emph{\bf phylogenetic relationship} &   &   &   \\

ABBA-BABA/D-statistics	 & biallelic SNP  &	Durand et al. 2011	 &  Heliconius Genome Consortium 2012 \\
fd statistic &	biallelic SNP &	Martin et al. 2015  &	Malinsky et al. 2015; Zhang et al. 2016 \\ 
five taxon D statistics	& biallelic SNP	&  Pease and Hahn 2015	& Fontaine et al. 2015; Pease et al. 2016 \\

\emph{\bf divergence} &   &   &   \\
Gmin &	biallelic SNP	&  Geneva et al. 2015	&  Kingan et al. 2015 \\
RNDmin	& phased haplotype	& Rosenzweig et al. 2016	&  NA \\
U and Q95	& biallelic SNP	& Racimo et al. 2016	 &  Sams et al. 2016 \\

\emph{\bf population structure related} &   &   &   \\
fineStructure &	phased haplotype &	Lawson et al. 2012	& Skoglund et al. 2015 \\
Globetrotter &	phased haplotype &	Hellenthal et al. 2014 & Scott et al. 2016 
\end{tabular}
\caption{Programs for identifying genomic regions under introgression \label{tab:tools}}
\end{figure}

%figure 1
\begin{figure*}[b]
\centering
\includegraphics{FigsAndTables/z2mIntroLoessRegression.pdf}
\caption{Loess regression of introgression level from \emph{mexicana} to Mexican Highland maize populations on chromosome 4 adapted from \cite{hufford2013genomic}.
\label{fig:maizeChr4Intro}}
\end{figure*}
